\section{Group Members Contribution}

\begin{description}
	\item[Alberto Basaglia]
Alberto was part of the design process of the ER diagram.
He wrote the logic that handles the dispatching of REST requests.
Additionally he wrote the part of the system that handles the management of the session and the authentication.
He reviewed the report and wrote the Presentation Logic Layer section.
	\item[Andrea Bruttomesso]
Andrea took part in designing the ER diagram and REST API endpoints to meet established standards.
Additionally, he assisted in crafting the REST request handling process.
Then played a role in developing Data Access Objects (DAOs) and endpoints for the Match entity. Moreover, Andrea implemented an automated system for generating matches, tailored for real-world applications.
Throughout the project, he actively engaged in code reviews, addressing minor issues, and suggesting improvements to enhance code style and readability.
	\item[Alessandro Corrò]
Alessandro worked on the initial setup of the presentation layer and gave a strong contribution in writing the report.
He wrote all the DAOs, Servlet and Handlers related to the Events and all the endpoints related to Match-Event handling.
	\item[Milica Popovic]
Milica wrote the first two sections of the report: Objectives and Main Functionalities.
Additionally, she helped with creating the ER diagram.
Furthermore, she created the sequence diagram, as well as all DAOs related to the Entity Type Team, and all the endpoints related to Team handling.
	\item[Davide Seghetto]
Davide wrote the first two parts of the report together with Milica, and also the third and fourth part.
He produced the presentation layer and the sample for the class diagram. Finally, he wrote the code for the RankingScorerServlet and for the DAOs
and the handlers related to the Tournament.
	\item[Andrea Stocco]
 Andrea contributed to the design of the ER diagram and wrote sections on REST API details and REST Error Codes.
He played a role in developing DAOs and endpoints to manage the Player entity and the tournaments ranking.
Finally, Andrea implemented the logic for uploading binary files to the database.
\end{description}