\section{Main Functionalities}

\noindent Our system accommodates three distinct user types:
\begin{itemize}
    \item Guest: a non-logged-in user.
    \item Team Administrator: a registered user responsible for managing his own teams.
    \item Tournament Administrator: a registered user responsible for managing his own tournaments.
    Additionally, tournament administrators can manage the teams enrolled in their tournaments.
\end{itemize}
A registered user may hold ownership of both tournaments and teams.
Every of those users can view past and present tournaments along with their related match schedules,
team standings, and other statistics.\\

\noindent More in-depth, the main functionalities are the following:
\begin{itemize}
    \item \textbf{Creation of a new tournament:}
        This functionality offers the opportunity to each logged in users to create a football tournament
        (and become its administrator).
        On the main page of the web app, it is possible to create an account which is required for the
        tournament creation. On the other hand, if the user already has an account he can proceed with the
        login step. After successfully completing the sign up or sign in process, there are other steps which
        should be taken such as providing basic data about the tournament (name, logo, deadline for the team
        creation, number of starting players, maximum number of players, maximum number of teams, etc.).
        Upon providing all essential data, the tournament is created and saved into the database. 
        
        \item \textbf{Edit/deletion of a tournament:}
        This feature enables a tournament administrator to edit data of the tournament or delete it.
        
    \item \textbf{Creation/edit/deletion of a team for the tournament:}
        Once the user is logged in, he can select the tournament of his interest in order to enroll
        his team by providing all data needed, such as a team name, logo, and players. Only the tournament and
        team administrator are allowed to edit the team data or delete the team.
        
    \item \textbf{Addition/edit/deletion of players:}
        Only the tournament and team administrator are allowed to add, edit, or delete players to/from
        the team.

    \item \textbf{Creation of the draw:}
        Tournament administrators have the ability to make a draw for the tournament. There are two options
        for making a draw: 
        \begin{enumerate}
            \item After the team creation deadline, the system will automatically make the tournament draw
            at midnight. This draw will then be available on the page.
            \item If the tournament administrator deems the tournament ready to start, he can choose to manually
            close subscriptions, at which point the system will promptly generate the matches.
        \end{enumerate}
        
    \item \textbf{Updating the info of a tournament's matches:}
        Only the tournament administrator is able to insert the result of a match that has been played,
        along with the main events like the scorers and the sanctions (yellow/red cards).
        
    \item \textbf{Following the tournament's matches:}
        Another feature of the webapp is displaying results of tournament matches and current statistics
        like team standings and top scorers' ranking. Users have the option to filter and view
        both concluded and upcoming matches. That feature is available for every active and past
        tournament, after choosing the particular tournament from the app's main page.

\end{itemize}
\newpage
